Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-10-10 analysis/paper/paper.qmd
add csv table

+-------+--------------------+---------+-------------+--------------------+-------------------------------------+----------------------------------------------------------+---------------+------------------+
| Phase | SP                 | Blades  | Micro-blade | SP Blank           | Newly added raw materials           | New changes                                              | Example sites | Radiocarbon ages |
+=======+====================+=========+=============+====================+=====================================+==========================================================+===============+==================+
| 1     | Present            | Absent  | Absent      | Flake              | Higher-quality quartzite,\          | Increasing number of small flake tools, appearance of SP | Hwadaeri\     | \~35 ka\         |
|       |                    |         |             |                    | Vein quartz                         |                                                          | Yonghodong\   | \                |
|       |                    |         |             |                    |                                     |                                                          | Sachang       |                  |
|       |                    |         |             |                    |                                     |                                                          |               |                  |
|       |                    |         |             |                    |                                     |                                                          | \             |                  |
+-------+--------------------+---------+-------------+--------------------+-------------------------------------+----------------------------------------------------------+---------------+------------------+
| 2     | Present            | Present | Present     | Blade              | Porphyry, Siliceous shale, Hitherto | Appearance of blades, increasing number of SP            |               | 35-25 ka         |
+-------+--------------------+---------+-------------+--------------------+-------------------------------------+----------------------------------------------------------+---------------+------------------+
| 3     | Present until 16ka | Present | Present     | Blade, Micro-blade | Obsidian                            | Appearance of Micro-blade, microliths                    |               | 25-12 ka         |
|       |                    |         |             |                    |                                     |                                                          |               |                  |
|       |                    |         |             |                    |                                     |                                                          |               | \                |
+-------+--------------------+---------+-------------+--------------------+-------------------------------------+----------------------------------------------------------+---------------+------------------+

: Korean Paleolithic Chronology edited based on Seong[-@seong2015diversity] and Park [-@Park_2013]

@@

@@

```
@tbl-landmark-abbreviations sth special~

@@

```
@tbl-cv-over-time says sth interesting

>>>>

@@

```{r}
#| label: tbl-korean-chronology
#| tbl-cap: Korean Paleolithic Chronology edited based on Seong[-@seong2015diversity] and Park [-@Park_2013]

here::here("analysis/data/raw_data/kr-paleolithic-chronology.csv") %>% 
  read.csv() %>% 
  knitr::kable(.)

@@

@tbl-landmark-abbreviations sth special\~

@@

@tbl-cv-over-time says sth interesting
